Rmarkdown Features

### 2018-04-12 Instructions/Rmarkdown_features/rmd_features.rmd
update

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: Apr 3, 2018
bibliography: /Users/user/local_depend/citation/neanderthals.bib
csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /Users/user/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 4
    toc_float: true
---

@@

About This Document {.tabset}
-----------------------------
### yaml of this Doc
```yaml
---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: /Users/user/local_depend/citation/neanderthals.bib
csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /Users/user/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 4
    toc_float: true
---
```

PDF Document (Chinese) {.tabset}
-----------------------------

### yaml

```yaml
---
output:
  pdf_document:
    latex_engine: xelatex    
    includes:
        in_header: header.tex
documentclass: article
urlcolor: "blue"
fontsize: 12pt
---
```

### header.tex
```tex
%加這個就可以設定字體
\usepackage{fontspec}
%使用xeCJK，其他的還有CJK或是xCJK
\usepackage{xeCJK}

@@

yaml Setup {.tabset}
-----------------------------
Include the code in yaml header.

### Citation

Include the code in yaml header.

```{yaml}
bibliography: ./citation/neanderthals.bib
csl: ./citation/apa-no-doi-no-issue.csl
link-citations: yes
```

### HTML Output Options

@@

![](mat2tex.png){width=85% height=auto .rounded}

@@

Citations 
-----------------------------

To include **Citations**, [Read this](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"}.

The text cited [@RN9].

@RN15 主張...

@@

@@

### Full Example
```{html}
<div class="success">
| This is pragraph one. [**Red text**]{.red}, line 1. Text text text text.
| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.

Paragraph two starts here.
</div>
```

<div class="success">
| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.

Paragraph two starts here.
</div>

### Colored divs
There are 4 choices of classes, defined in my stylesheet[^css]:

@@

```{html}
<div class="info">
some text in the colored region
</div>
```

<div class="info">
some text in the colored region
</div>

Alternatively, you can use bootstrap's default alert divs, defined by four classes:

1. alert-success
2. alert-warning
3. alert-info
4. alert-danger
```{html}
<div class="alert alert-success">
some text in the colored region
</div>
```

<div class="alert alert-success">
Bootstrap-defined colored region
</div>

@@

<div class="warning">
| Text of line 1
| Text of line 2

New paragraph
</div>

@@

#### `class`
```{markdown}
[**Red Bold text**]{.red}
```
<div class="warning">
[**Red Bold text**]{.red}
</div>

@@

#### Other Attributes
```{markdown}
Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
```
<div class="warning">
Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
</div>

@@

    Subsequent paragraphs are indented to show that they
belong to the previous footnote.

    In this way, multi-paragraph footnotes work like multi-paragraph list items.
```
- Output[^longnote].

@@

### Rounded Edge
```{html}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
```
![](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}

### Circle Image
```{html}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
```
![This is figure Caption](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}

@@

    Subsequent paragraphs are indented to show that they
belong to the previous footnote.

>>>>

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: "`r Sys.Date()`"
bibliography: /Users/user/local_depend/citation/neanderthals.bib
csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /Users/user/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 3
    toc_float:
        collapsed: false
---

@@

yaml Setup {.tabset}
-----------------------------

yaml metadata determines the output file format, looking, and any other additional customizing features of Rmarkdown files.

### yaml of this Doc

This is the complete yaml header of this document.

```yaml
---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: /Users/user/local_depend/citation/neanderthals.bib
csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /Users/user/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 3
    toc_float:
        collapsed: false
---
```

### HTML Output

### PDF Output

You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
```yaml
---
output:
  pdf_document:
    latex_engine: xelatex    
    includes:
        in_header: header.tex
documentclass: article
urlcolor: "blue"
fontsize: 12pt
---
```

### PDF: header.tex{#pdf-header}

The code below is for generating PDF documents written in (Traditional) Chinese.

```tex
%加這個就可以設定字體
\usepackage{fontspec}
%使用xeCJK，其他的還有CJK或是xCJK
\usepackage{xeCJK}

@@

### Bibliography

```{yaml}
bibliography: ./citation/neanderthals.bib
csl: ./citation/apa-no-doi-no-issue.csl # APA style sheet
link-citations: yes
```

For citation syntax, read the section [Bibliography & Citations](#cite).

@@

![](mat2tex.png){width=100% height=auto}

@@

Bibliographies & Citations{#cite} 
-----------------------------

You can read the full documentation of [Bibliographies & Citations](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"} at Rstudio.

### Citation syntax

#### Classical Citation: **Author**, **year**, and **brackets**
- `Some text [@Bib.ID].`
    - Some text [@RN9].

#### In-text Citation: **Author (year)**
- `@Bib.ID Some text`
    - @RN15 Some text

- `@Bib.ID [p. 20] Some text.`
    - @RN9 [p. 20] Some text.

#### Year only: Suppress Author
- `Some text [-@Bib.ID].`
    - Some text [-@RN9]

#### Two Citations
- `Some text [@Bib.ID1; @Bib.ID2].`
    -  Some text [@RN9; @RN15].

5. Prefix & Suffix
    - `Some text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
        -  Some text [see @RN9 pp. 45; also, @RN15 ch. 2].

@@

Rmarkdown requires specific formats of bibliographies. One of the most common one is `.bib`. A lot of people (including me) use Endnote to manage bibliographies and have no time getting used to other open source reference managers. Read  [this](https://libguides.usask.ca/c.php?g=218034&p=1458583) to see how to generate `.bib` from EndNote.

Below are some syntax in Rmarkdown to control the display of reference in the document.

#### Reference heading

The body of cited reference in the `.bib` file will be shown under the header named Reference (it doesn't matter which **level** of heading you use).

```markdown
## Reference
```

@@

### An Example

````markdown
`r ''````{block2, type="success"}
| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.

Paragraph two starts here.
```
````

```{block2, type="success"}
| This is line 1, pragraph one. [**Red text**]{.red}. Text text text text.
| This is [line 2]{style="color:rgba(255, 0, 0, 1)"} of paragraph one.

Paragraph two starts here.
```

### Colored divs

You can use bootstrap's default alert divs in Rmarkdown, defined with four classes:

1. alert alert-success
2. alert alert-warning
3. alert alert-info
4. alert alert-danger

````markdown
`r ''````{block, type="alert alert-success"}
Bootstrap-defined colored region
```
````

```{block, type="alert alert-success"}
Bootstrap-defined colored region
```

#### Customized divs

Alternative, you can define your own styled divs, as in my stylesheet[^css]:

There are 4 choices of classes,

@@

````markdown
`r ''````{block, type="info"}
some text in the colored region
```
````

```{block, type="info"}
some text in the colored region
```

### Bootstrap Callouts

Althougt it's "Bootstrap" callouts, it's not contained in default bootstrap theme. I defined it in my stylesheet.

There are 4 choices of classes,

1. bs-callout bs-callout-success
2. bs-callout bs-callout-warning
3. bs-callout bs-callout-info
4. bs-callout bs-callout-error

````markdown
`r ''````{block2, type="bs-callout bs-callout-warning"}
#### Heading in Callout
**Calleout Text** texttexttexttexttexttext
```
````

```{block2, type="bs-callout bs-callout-warning"}
#### Heading in Callout
**Calleout Text** texttexttexttexttexttext
```

@@

```{block2, type="alert alert-success"}
| Text of line 1
| Text of line 2

@@

#### `class`

Rmarkdown syntax allows attaching attributes (such as class, id, etc.) to certain elements by wrapping attributes into `{ ... }`.

Elements allowed attributes to be attach (by markdown syntax directly):

1. Section: Attributes are added next to **any level of heading**.
2. Link: `[Text](LINK){attributes}`
3. `span`: Text wrapped in `[`, `]`. e.g `[Text with class "red"]{.red}`.

```{markdown}
[**Red Bold text**]{.red}
```

```{block2, type="alert alert-success"}
[**Red Bold text**]{.red}
```

@@

#### Other Attributes
```{markdown}
Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
```

```{block2, type="alert alert-success"}
Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
```

@@

    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).

    In this way, multi-paragraph footnotes work like multi-paragraph list items.
```
- Read the output by clicking the superscript[^longnote].

@@

### Rounded Edge
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
```
![](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}

#### Boostrap
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
```
![Bootstrap Rounded](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}

### Circle Image
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
```
![This is figure Caption](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}

#### Boostrap
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
```
![Bootstrap Circle](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}

### Thumbnail
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
```
![Bootstrap Thumbnail](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}

@@

    Subsequent paragraphs are indented to show that they belong to the previous footnote. (JUST IGNORE ME, I AM Exteeeeeendiiiiiiing the text to show the effect of paragraph).
